Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-11-13 paper/introduction.tex
Update paper.

Guided proofreading is applicable to all existing automatic segmentation methods that
produce a label map. As such, we believe that our approach is a promising
direction to proofread segmentations more efficiently and better tackle large
volumes of connectomics imagery.

>>>>

Guided proofreading is applicable to all existing automatic segmentation methods that
produce a label map.
\CHANGED{While we train models based on traditional CNN architectures, we propose an error correction framework with human interaction that works in principle with any potential classifier.}
As such, we believe that our approach is a promising direction to proofread segmentations more efficiently and better tackle large volumes of connectomics imagery.

### 2017-11-13 paper/results.tex
Update supplemental material.
Update paper.

%We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings. Lower VI scores indicate less distance to the ground truth and a better segmentation. For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
Additional plots and confirmatory data analysis are available as supplemental material due to limited space.

@@

\paragraph{Subjective responses.} We used the NASA-TLX workload index to record subjective responses. Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading. However, these differences were not statistically significant. This is unsurprising as the user interface was the same for both groups.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
\caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across slices of the AC4 subvolume, with different error correction approaches. The variation resulting from performance of FP with automatic selection is $4.5\times$ higher than GP (as indicated by the arrow), with median VI of $1.9$ and $SD=0.496$.}
\label{fig:ac4boxplot}
\end{figure}

>>>>

%We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings. Lower VI scores indicate less distance to the ground truth and a better segmentation. For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
Additional plots \CHANGED{and confirmatory data analysis} are available as supplemental material due to limited space.

@@

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
\caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across slices of the AC4 subvolume, with different error correction approaches. The performance of FP with automatic selection is $4.5\times$ higher than GP (\protect\includegraphics[width=0.2cm]{gfx/arrow.pdf}), with median VI of $1.9$ and $SD=0.496$.}
\label{fig:ac4boxplot}
\end{figure}
